Does a fully convective star need a special corona to produce a polar flare?

### 2023-06-29 src/tex/ms.tex
[showyourwork] overleaf sync

% Main body with filler text
\section{Introduction}
\label{sec:intro}
The smallest stars are crawling with rocky planets. The mass of the disk decreases such that giant planet are no longer efficiently formed, leaving room for smaller objects in the orbit. Terrestrial planets in the habitable zones of these stars are a factor of XXXX more likely than around higher mass stars. However, to be truly habitable in an Earth-like sense, more conditions need to be met than simply the possibility of surface water in its liquid form. One of them is the space weather of the host, that is, the high energy radiation and particles that force the planet's atmosphere. If too high, the atmosphere may blow off. If too energetic, life may not survive. If not energetic enough, life may not emerge in the first place. So, what is the space weather of planets around these smallest, and most abundant, stars, like?

At the lowest masses, a star's life unfolds much slower than for a Sun. While the Sun's magnetic activity, and with it the flares, winds, coronal mass ejections and energetic particle eruption that make up space weather, decline rapidly over a few hundred megayears, a fully convective M dwarf stays highly active for gigayears. Add that the zone where liquid water can reside is much closer to these faint stars, and the result is a planet that may be exposed to violent space weather conditions for a good fraction of the age of the universe.

Space weather originates from the stellar corona. The transition from star to brown dwarf is characterized by increasing rotation speed and decreasing coronal emission. The simultaneous surge of radio emission indicates a transition from stellar corona to planet-like magnetosphere at the bottom of the main sequence. Yet, brown dwarfs are regularly detected with energetic flares regardless of their low X-ray luminosity. How these flares are produced in the apparent absence of a solar-type corona is unclear. An intermittent corona is conceivable, similarly XYZ. Perhaps, the rapid rotation of these low-mass objects plays a role, as it governs the dynamo process within.

@@

\begin{figure}
    \script{FIGURE_tess_ffd.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/tess_ffd.png}
        \caption{
         Flare frequency distribution and power law fit.
        }
        \label{fig:ffd}
    \end{centering}
\end{figure}

>>>>

% Main body with filler text
\section{Introduction}
\label{sec:intro}
The smallest stars are crawling with rocky planets. The disk mass around the smallest stars decreases such that giant planets are no longer efficiently formed, leaving room for smaller objects in the orbit~(XXXX). Terrestrial planets in the habitable zones of these stars are a factor of XXXX more likely than around higher mass stars~\citep{hardegree-ullman2019kepler}. However, to be habitable in an Earth-like sense, merely the possibility of surface water in its liquid form does not suffice. Space weather of the host, that is, the high energy radiation and particles that force the planet's atmosphere, is another important factor. If the energetic particle flux is too high, the atmosphere may blow off. If not energetic enough, life may not emerge in the first place.

At the lowest masses, a star's evolution unfolds much slower than for a Sun. While the Sun's magnetic activity, and with it the flares, winds, coronal mass ejections and energetic particle eruption that make up space weather, decline rapidly over a few hundred megayears, a fully convective M dwarf stays highly active for gigayears. Add that the zone where liquid water can reside is much closer to these faint stars, and the result is a planet that may be exposed to violent space weather conditions for a good fraction of the age of the universe.

Space weather originates from the stellar corona. The transition from star to brown dwarf is characterized by increasing rotation speed and decreasing coronal emission. The simultaneous surge of radio emission indicates a transition from stellar corona to planet-like magnetosphere at the bottom of the main sequence. Yet, brown dwarfs are regularly detected with energetic flares regardless of their low X-ray luminosity. How these flares are produced in the apparent absence of a solar-type corona is unclear. An intermittent corona is conceivable, similarly XYZ. Perhaps, the rapid rotation of these low-mass objects plays a role, as it governs the dynamo process within, and consequently influences the complex process of flux emergence~\citep{weber2023understanding}.

@@

\begin{figure}
    \script{FIGURE_tess_ffd.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/277539431_tess_ffd.png}
        \caption{
         Flare frequency distribution and power law fit.
        }
        \label{fig:ffd}
    \end{centering}
\end{figure}
